The globular cluster system of the Auriga simulations

### 2019-08-16 AurigaGCS.tex
Acknowledgements: remarks FM + RG. Thanks MPCDF for Freya

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.
\todo[inline]{Check Auriga boilerplate that we need to acknowledge}
RG and VS acknowledge support by the DFG Research Centre SFB-881 `The
Milky Way System' through project A1. This work has also been
supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the
SuperMUC system at the Leibniz Computing Centre, Garching,
under the project PR85JE of the Gauss Centre for Supercomputing.
This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology
on behalf of the STFC DiRAC HPC Facility `www.dirac.ac.uk'.
This equipment was funded by BIS National E-infrastructure capital
grant ST/K00042X/1, STFC capital grant ST/H008519/1 and
STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.

>>>>

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS)
on Astrophysics. TLRH thanks the Max Planck Computing and Data Facility for
maintaining the Freya compute cluster, where the simulations were post-processed.
FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR.
This work has been supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the SuperMUC system 
at the Leibniz Computing Centre, Garching, under the project PR85JE of the Gauss 
Centre for Supercomputing. This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology on behalf of
the STFC DiRAC HPC Facility `www.dirac.ac.uk'. This equipment was funded by BIS 
National E-infrastructure capital grant ST/K00042X/1, STFC capital grant 
ST/H008519/1 and STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.
